---
title: "Assignment 4 - Applying meta-analytic priors"
author: "Riccardo Fusaroli"
date: "3/16/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

getwd()
locpath= getwd()
setwd(locpath)

library(pacman)
p_load(ggplot2, rethinking, readxl, brms, metafor, tidyverse, lme4)

d = read_excel("Assignment4PitchDatav2.xlsx")
d_meta = read_excel("Assignment4MetaData.xlsx")

```

## Assignment 4

In this assignment we do the following:
- we reproduce the meta-analysis of pitch SD from last semester in a Bayesian framework
- we reproduce the pitch SD in schizophrenia analysis from last semester using both a conservative and a meta-analytic prior
- we assess the difference in model quality and estimates using the two priors.

The questions you need to answer are: What are the consequences of using a meta-analytic prior? Evaluate the models with conservative and meta-analytic priors. Discuss the effects on estimates. Discuss the effects on model quality. Discuss the role that meta-analytic priors should have in scientific practice. Should we systematically use them? Do they have drawbacks? Should we use them to complement more conservative approaches? How does the use of meta-analytic priors you suggest reflect the skeptical and cumulative nature of science?

### Step by step suggestions

Step 1: Reproduce the meta-analysis of pitch sd from previous studies of voice in schizophrenia
- the data is available as Assignment4MetaData.xlsx
- Effect size (cohen's d), sd and variance are already calculated (you're welcome!)
- Since we're only interested in getting a meta-analytic effect size, let's take a shortcut and use bromance magic (brms): https://mvuorre.github.io/post/2016/2016-09-29-bayesian-meta-analysis/

```{r}

# m <- BRM(MeanES|SE(SdES)) ~ 1 + (1|StudyREF), 
#         # Prior = # the computer will compute the best prior by itself 
#         Data = d_meta
#         Cores = 2 # has to do with the computer, we'll run the model(s) on two processors/cores??
#         Chain = 2 # again somehitng woth the computer and maybe 2 processes
#         ITER = 2000
# # Dealing with the Cohens d
# standardize over all wtudies to top_n(scale)
# mean group 1 - minus - studies mean of model 2 = pooled SD
# the more unsertain - delete - make it balande - the storinger/dloset to a normai voidse, the 
# 


model <- brm(MeanES|se(SdES) ~ 1 + (1|StudyRef), data = d_meta, prior = NULL, chains = 2, iter = 2000, cores = 2)
summary(model)

# making a forestplot to visualize data
m1 = rma(yi = MeanES, vi = SdES, data = d_meta, slab = StudyRef)
forest(m1)


# to do:
# forest plot 
# look at estimates and error (does the meta analytic effect look gaussian?)
# this is a simulation (?)
# the numbers are our uncertainties (-0.55 and 0.25)
# we want to eliminate the need to use random effects (we only want 1 data point per participant)
# - idea: group by id and summarise mean ?? (then we have a mean for each participant)

#standardize the data
library(dplyr)
d_s = scale(d, center = TRUE, scale = TRUE)
d_s = as.data.frame(d_s)

#take the mean of pitch SD for each participant, so we don't have to use random effects in our model (from 10 datapoints to 1)
Unique_PitchSD = d_s %>% 
  group_by(ID) %>% 
  summarise(Unique_PitchSD = mean(PitchSD))
  
d_s = merge(d_s,Unique_PitchSD)


```


BRM is instead of the glmer
outcome: mean effc´effect size 
=z
meanES (mean effect size)
MeanEs | SdEs 



Step 2: Prepare the pitch SD data from last year
- the data is available as Assignment4PitchData.csv (thanks Celine)
- We do not know how to build random effects, yet. So we need to simplify the dataset to avoid interdependence between datapoint: How?
- Also, let's standardize the data, so that they are compatible with our meta-analytic prior (Cohen's d is measured in SDs).

Step 3: Build a regression model predicting Pitch SD from Diagnosis.
- how is the outcome distributed? (likelihood function)
- how are the parameters of the likelihood distribution distributed? Which predictors should they be conditioned on?
- use a skeptical/conservative prior for the effects of diagnosis. Remember you'll need to motivate it.
- Describe and plot the estimates. Evaluate model quality

```{r}
# making a data frame with only unstandardised ID and diagnosis and unique pitch SD 
data = cbind(d$ID, d$diagnosis, d_s$Unique_PitchSD)

# rename column names
colnames(data) <- c("ID", "diagnosis", "Unique_PitchSD")

# removing duplicated rows
data = data[!duplicated(data), ]

# making it a data frame 
data = as.data.frame(data)

# Build a regression model predicting Pitch SD from Diagnosis (w the brm function)
model <- brm(Unique_PitchSD ~ 1 + diagnosis, data = data, prior = NULL, chains = 2, iter = 2000, cores = 2)
summary(model)

# Build a regression model predicting Pitch SD from Diagnosis (w the MAP function)
# posterior <- likelihood * prior 

# Pi ~ Normal(µ,sigma)   = likelihood
# µ ~ Normal(mean, SD)   = µ prior
# sigma ~ Uniform(0,50)  = sigma prior 

model <- map(
  alist(
    Unique_PitchSD ~ dnorm(mu, sigma) ,
    mu <- a + bD*diagnosis ,
    a ~ dnorm(0,1) , #relates to Unique_PitchSD (predictee)
    bD ~ dbinom() ,
    sigma ~ 

#a skeptic prior = .1 on the beta value 
#what is a difference of .6? 
#what is a cohen's d of .6? - it tells us that the difference between the 2 groups is a .6 (in SD) 
#choices that you can defend - .2 and .5 they are legitimate priors but not skeptic - a prior of .2 
#gaussian - between -1.56 to 1.96 
#meaning that SD covers 4 
# 3 SD on each side coers the 95 confidence intercal / here you'll find 
# what we expect to see is the mean of the true underlying effect
# SD = square root of variance - how much they deciate-  coorected for no of studies
# each of these estimates are also applicaple? 
# SD bigger tnan mean = bad data
SD(nt)
h´b deals wiht 
# SE = 






```


Step 4: Now re-run the model with the meta-analytic prior
- Describe and plot the estimates. Evaluate model quality

Step 5: Compare the models
- Plot priors and posteriors of the diagnosis effect in both models
- Compare posteriors between the two models
- Compare their relative distance from truth (WAIC)
- Discuss how they compare and whether any of them is best.

Step 6: Prepare a nice write up of the analysis and answer the questions at the top.

Optional step 7: how skeptical should a prior be?
- Try different levels of skepticism and compare them using WAIC.

Optional step 8: Include other predictors
- Do age, gender and education improve the model?
- Should they be main effects or interactions?

Optional step 9: Bromance magic.
- explore the bromance code below including random effects (by default with weakly informative priors)
- learn how to change the prior
- explore effects of trial, age, gender, including the appropriate random slopes
- compare the models you created using WAIC and posterior predictive check (pp_check())


```{r}

brm_out <- brm(PitchSD ~ 1 + Diagnosis  +(1|ID_unique/Study), # Outcome as a function of the predictors as in lme4. 
               data=Data, # Define the data
               family=gaussian(), # Define the family. 
               iter = 5000, warmup = 2000, cores = 4)
summary(brm_out1)
plot(brm_out1)

```

